|

### 2022-07-03 manuscript.Rmd
fix yaml affiliation
one sentence per line
use md-style italics

---
title: |
  Teaching Visual Accessibility in the Introductory Data Science Classes: Why, What, When, and How
shorttitle: Teaching Accessibility in Data Science
author:
- name: JooYoung Seo
  affiliation: "1"  # Must be quoted when including comma.
  email: "jseo1005@illinois.edu"  # Only corresponding authors require email.
- name: Mine Dogucu
  affiliation: 2,3

@@

According to LinkedIn's 2017 U.S. Emerging Jobs Report, machine learning engineers and data scientists rank among the top emerging jobs.
With the urgent need for training a higher number of skilled data scientists, many institutes of higher education are developing their own data science curricula and a consensus on what should be included in such curricula has not yet been reached. In the latest version of \textit{Computing Competencies for Undergraduate Data Science Curricula} by ACM Data Science Task Force, accessibility is a recommended content for the data science curricula \cite{danyluk2021computing}.

>>>>

---
title: |
  Teaching Visual Accessibility in the Introductory Data Science Classes: Why, What, When, and How
shorttitle: Teaching Accessibility in Data Science
author:
- name: JooYoung Seo
  affiliation: "1"  # Must be quoted when including comma.
  email: "jseo1005@illinois.edu"  # Only corresponding authors require email.
- name: Mine Dogucu
  affiliation: "2,3"

@@

According to LinkedIn's 2017 U.S. Emerging Jobs Report, machine learning engineers and data scientists rank among the top emerging jobs.
With the urgent need for training a higher number of skilled data scientists, many institutes of higher education are developing their own data science curricula and a consensus on what should be included in such curricula has not yet been reached. 
In the latest version of *Computing Competencies for Undergraduate Data Science Curricula* by ACM Data Science Task Force, accessibility is a recommended content for the data science curricula \cite{danyluk2021computing}.
